A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-12-09 doc/review-acom/response-to-referees.tex

\begin{document}

\maketitle

In this document, we respond to the referees' comments
for the paper ``A boundary integral equation approach to computing
eigenvalues of the Stokes operator''.
We believe that the referees' suggestions improve the
quality of the paper and that we have been able to
address their concerns. Changes made to address these concerns
are marked in {\color{red} red} in the revised manuscript.

We have also marked in {\color{red} red} a couple of
changes around the explanation of the order of convergence
of the generalized Gaussian quadrature rule we used.
The rule is designed to be 16th order, i.e. it is designed
to integrate $p(y)\log|x-y| + q(y)$ for $p$ and
$q$ polynomials of degree up to 15. Our kernel is actually
smoother than $\log|x-y|$ (with leading order
singularity $|x-y|^2\log|x-y|$) and in our experience the
convergence rate is typically higher (20th order in
the example in the paper). In the revised text, we have clarified
that the rule is not designed to be 20th order but that this is
the behavior we observed.

### 2019-12-09 doc/review-acom/stokes-eig.tex
update quadrature rule language

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the {\color{red} 16th-order} rule we used
{\color{red} (i.e. a rule which integrates
  $p(\yy)\log|\xx-\yy| + q(\yy)$ for $p$ and $q$
  polynomials of degree up to 15)}, $N_s = 16$ and
  $N_a = 48$. 
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

@@

The compressed representation also allows
for fast applications of the system matrix,
its transpose, the inverse of the system
matrix, and the inverse transpose to
vectors.
%
In particular, this allows us to estimate the
smallest singular values by performing
randomized subspace iteration, see
\cite[Algorithm 4.4]{halko2011finding},
on the inverse operator.
%
Below, we use the smallest singular value
as a measure of the quality of the
eigenvalues found by approximating the
roots of the determinant.
%
We also evaluate the second smallest singular
value to check for possible double eigenvalues.

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Recall that the GGQ we use {\color{red} is designed to
evaluate integrals of the form $p(\yy)\log|\xx-\yy|
+ q(\yy)$ with $p$ and $q$ polynomials of degree up
to 15, so that the observed convergence rate
for the roots is of slightly higher order than the
order of the quadrature rule. In our experience, the $N^{-20}$
rate is common for these kernels and may be a result of the
fact that the singularity for these kernels is of the form
$|\xx-\yy|^2\log|\xx-\yy|$, which is smoother than
$\log|\xx-\yy|$ itself.}
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

>>>>

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the {\color{red} 16th-order} rule we used
{\color{red} (i.e. a rule which integrates
  $\Phi(s)\log|t-s| + \Psi(s)$ over $[-1,1]$ exactly
  for $\Phi$ and $\Psi$ polynomials of degree up
  to 15)}, $N_s = 16$ and
  $N_a = 48$. 
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

@@

The compressed representation also allows
for fast applications of the system matrix,
its transpose, the inverse of the system
matrix, and the inverse transpose to
vectors.
%
In particular, this allows us to estimate the
smallest singular values by performing
randomized subspace iteration, see
\cite[Algorithm 4.4]{halko2011finding},
on the inverse operator.
%
Below, we use the smallest singular value
as a measure of the quality of the
eigenvalues found by approximating the
roots of the determinant.
%

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Recall that the GGQ we use {\color{red} is 16th order
  for $\log$ singularities, so that the observed convergence
  rate for the roots is of higher order than the
  order of the quadrature rule. This behavior is a bit
  surprising but may owe to the fact that the integral
  kernels are actually smoother than $\log|\xx-\yy|$
  (with leading order singularity $|\xx-\yy|^2\log|\xx-\yy|$).
  Alternatively, the asymptotic convergence rate may simply
  not be apparent before the maximum precision is reached.}
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.
